\documentclass{article}
\usepackage{../fasy-hw}
\usepackage{ wasysym }

%% UPDATE these variables:
\renewcommand{\hwnum}{1}
\title{Computational Topology, Homework 1}
\author{~}
\collab{n/a}
\date{1/18--2/29}

\begin{document}

\maketitle

\section*{The Six-Week Assignment}

This assignment will cover the first six weeks of this class.

Please complete the following:
\begin{enumerate}
    \item Pre-assessment. Answer the following questions without looking up the
        answers.  Then, chat with a classmate (who has completed this), with a
        CompTaG member, and/or
        look up the answers. Give yourself constructive feedback: what did you
        get right/wrong, and what things do you need to work on? Provide
        citations for resources used, and make note of people that you have
        conversations with. Note that you are not expected to know all of these
        answers yet, but if you do not know these terms, please use this as a
        hint that you are now expected to know them.
        This should be completed by 1/19 and posted to D2L (including both your
        original answers and your feedback to yourself).  This can be typed
        up, or handwritten and scanned.  The upload must be a PDF though.
        \begin{enumerate}
            \item Prove that a tree with $n$ nodes has $n-1$ edges.
            \item Define the following terms: even number, connected component,
                graph, group, field, topological space, continuous function.
            \item For the following, explain what they are in the context of
                algorithms (e.g., what are common operations that would be
                performed and how long do those operations take): list, stack, queue,
                array, hash table.
            \item Define big-O notation and worst-case analysis.
        \end{enumerate}
    \item Onboarding tasks.  Please complete the onboarding tasks found here:
        \url{https://github.com/compTAG/student-resources/blob/master/how-tos/onboarding.md}.
        These are designed for students interested in research in Computational
        Topology and Geometry, but working through this list will be helpful for
        you too!
    \item Weekly Journal.
        These are the expectations for each week of the class:
        \begin{enumerate}
            \item Skim through the reading material of the week.
            \item Meet with each other to discuss the readings and to work on the
                problems.  Problems that you can work on are listed in this document.
                Often, to really understand the material, you need to work through
                problems, not just read. You can use the designated meeting time and
                location, the CompTaG labspace, and the class zoom as needed for these
                meetings. As with any graduate class, you are expected to work about 3
                hours outside of class for every hour in class.
            \item Ask questions! I expect each student in the class to ask and to answer
                at least one question per week on slack.  The question can be directed
                to \#csci535-sp24 or \#technical. If you do not have a specific question,
                you may also post something cool that you learned this week, or to
                provide additional resources that you found especially helpful that
                week.
            \item Go back to the week's reading and really dive into the reading
                material of the week.
            \item Journal: Write a summary of what you did this week, including (at a
                minimum) a list of things that you did and a list of questions that you
                still have. If you want, your journal can include
                answers to problems from the text (or portions of them).  Put
                this journal entry in a LaTex file, and add to it each week.  The
                journal is what you will hand in at the end of the first six weeks of
                class.  \color{blue}{\bf At the end of your journal, please provide two to four
                questions about computational topology that you have at this point.
                These questions should be in blue}.
        \end{enumerate}
\end{enumerate}

\section*{Problems}

These will not be formally collected, but working through the following problems
will be helpful for your learning.  If guest lecturers provide problems to work
through, please add them to this list!

\begin{itemize}
    \item Week 1/2
        \begin{itemize}
            \item \todo{}
        \end{itemize}
    \item Week 3
        \begin{itemize}
            \item \todo{}
        \end{itemize}
    \item Week 4
        \begin{itemize}
            \item \todo{}
        \end{itemize}
    \item Week 5
        \begin{itemize}
            \item \todo{}
        \end{itemize}
    \item Week 6
        \begin{itemize}
            \item \todo{}
        \end{itemize}
    \item Week 7
        \begin{itemize}
            \item \todo{}
        \end{itemize}
\end{itemize}

\end{document}
