\documentclass[a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{amsmath, amssymb, amsthm}

\usepackage{setspace}
\usepackage{tikz}

\usetikzlibrary{automata, arrows, chains}
\tikzset{
	>=stealth, % makes the arrow heads bold
	node distance=3cm, % specifies the minimum distance between two nodes. Change if necessary.
	every state/.style={thick, fill=gray!10}, % sets the properties for each ’state’ node
	initial text=$ $, % sets the text that appears on the start arrow
	in place/.style={
		auto=false,
		inner sep=3pt,
	},
}


\title{Computational Topology Journal}
\date{Weeks 1-7}
\author{Jack Ruder}


\begin{document}

\doublespacing
\maketitle
\section{Week 1}
This week was mostly just getting acquainted with MSU so I didn't do as much as I would have liked. I did the pre-assessment and a handful of the problems in the Edelsbrunner-Harer book to jog my memory. Also, I worked on the onboarding and put some work into the TDA r-script from the workshop (though my quest to abstract my code has not gone well, R and I do not get along well).

\section{Week 2}
The focus this week was in getting comfortable with nerves, homotopy equivalence, and proving things about simplicial complexes. I worked on the listed problems, and managed to arrive at solutions to each of them, but struggled more to formally state the solutions. It was hard to tell if I was just overcomplicating the proofs? Either way I got very comfortable with the definitions and ideas in the readings. No huge questions at this point.

\section{Week 3}
Week 3 we reviewed homology. Tuesday in 'class' we computed homology groups of simplicial complexes for practice, and computed the boundary matrices. I worked on Dey-Weng Ch.2 problem 3, as well as the first two Edelsbrunner problems. I still feel a bit shaky on intuitively understanding homology groups, but I am solid on cycle groups and boundary groups (intuitively). I understand why homology groups give holes by working through lots of examples but I just need more time with these topics. I did not get as much done as I wanted this week (maybe about 5 hours outside of class) so hopefully next week I can get more done and feel more comfortable.
Somehow my R script from the workshop completely broke (again) so I rewrote a much simpler version with a mini-analysis at the end.

\end{document}
